---
title: "Assignment 2"
---

This assignment is about "Web Scraping of Turkish Movies from IMDB" You can see the desired codes and outputs below.

I did my best on this assignment, and for some parts of the code, I used AI assistance, which I have mentioned.

# The Code for Question 1,2,3

```{r}
install.packages("tidyverse")  
install.packages("rvest")    
install.packages("ggplot2")

library(tidyverse)
library(rvest)
library(stringr)
library(ggplot2)

# Urls for the films, first url belongs to 2010-2023, second one belongs to below 2010.
urls <- c(
  "https://m.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-31&num_votes=2500,&country_of_origin=TR&count=250",
  "https://m.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"
)

# Scrapping the movies
scrape_movie_data <- function(url) {
  page <- read_html(url)
 
  titles <- page %>% html_nodes(".ipc-title__text") %>% html_text()
  years <- page %>% html_nodes(".dli-title-metadata-item:nth-child(1)") %>% html_text()
  durations <- page %>% html_nodes(".dli-title-metadata-item:nth-child(2)") %>% html_text()
  ratings <- page %>% html_nodes(".ratingGroup--imdb-rating") %>% html_text()
  votes <- page %>% html_nodes(".ipc-rating-star--voteCount") %>% html_text()
 
  #Check the lengths and correct any inconsistencies(I got AI help here, to aviod errors.)
  print(paste("Number of Titles:", length(titles)))
  print(paste("Number of Years:", length(years)))
  print(paste("Number of Durations:", length(durations)))
  print(paste("Number of Ratings:", length(ratings)))
  print(paste("Number of Votes:", length(votes)))
 
  #I got AI help here, to aviod errors.
  max_length <- max(length(titles), length(years), length(durations), length(ratings), length(votes))
  titles <- rep(titles, length.out = max_length)
  years <- rep(years, length.out = max_length)
  durations <- rep(durations, length.out = max_length)
  ratings <- rep(ratings, length.out = max_length)
  votes <- rep(votes, length.out = max_length)
 
  # Convert the durations to minutes (convert hours and minutes to total minutes)
  duration_minutes <- str_extract(durations, "\\d+(?=h)") %>%
    as.integer() * 60 + str_extract(durations, "\\d+(?=m)") %>% as.integer()
 
  #I got AI help here, to aviod errors.
  votes_cleaned <- str_remove_all(votes, "[^0-9.KM]") %>%
    str_replace_all("K", "e3") %>%  # 1K -> 1000, 1.5K -> 1500
    str_replace_all("M", "e6") %>%  # 1M -> 1000000
    as.numeric()
 
  #I got AI help here, to aviod errors.
  ratings_cleaned <- str_replace_all(ratings, "\\(.*\\)", "") %>%
    str_trim() %>% as.double() %>% replace_na(NA)
 
  #Data Frame Creating
  movie_data <- tibble(
    Title = titles,
    Year = years,
    Duration = duration_minutes,
    Rating = ratings_cleaned,
    Votes = votes_cleaned
  )
 
  return(movie_data)
}

# Fetching data from both URLs
movie_data1 <- scrape_movie_data(urls[1])
movie_data2 <- scrape_movie_data(urls[2])

#Combining the datas
combined_movie_data <- bind_rows(movie_data1, movie_data2)

print(head(combined_movie_data))
#Top 5 ranked movies
top_rated_movies <- combined_movie_data %>%
  arrange(desc(Rating)) %>%
  head(5)

print("Top 5 Ranked Movies:")
print(top_rated_movies)

#Bottom 5 ranked movies
lowest_rated_movies <- combined_movie_data %>%
  arrange(Rating) %>%
  head(5)

print("Bottom 5 Ranked Movies:")
print(lowest_rated_movies)
fav_movies <- c("A.R.O.G", "G.O.R.A.")

fav_movie_data <- combined_movie_data %>%
  filter(Title %in% fav_movies) %>%
  select(-Duration) %>% # Remove 'Duration' column as per your previous code
  arrange(desc(Rating))
print(fav_movie_data)
#The average rating and total number of films by year
updated_movie_data <- combined_movie_data %>%
  group_by(Year) %>%
  mutate(Mean_Rating = mean(Rating, na.rm = TRUE), Total_Film_Count = n())

# Yıllara göre ortalama puan grafiği (sütun)
plot_mean_rating_year_col <- updated_movie_data %>%
  ggplot(aes(x = Year, y = Mean_Rating)) +
  geom_col() +
  theme_minimal() +
  labs(title = "Average Rating by Year", x = "Year", y = "Average Rating")

print(plot_mean_rating_year_col)

plot_mean_rating_year_point <- updated_movie_data %>%
  ggplot(aes(x = Year, y = Mean_Rating)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Average Rating by Year (Point)", x = "Year", y = "Average Rating")

print(plot_mean_rating_year_point)

# (boxplot)
plot_rating_distribution_year_box <- updated_movie_data %>%
  ggplot(aes(x = Year, y = Rating)) +
  geom_boxplot() +
  theme_minimal() +
  labs(title = "Average Rating by Year", x = "Year", y = "Rating")

print(plot_rating_distribution_year_box)

# Total Number of Films by Year Chart
plot_total_film_count_per_year <- updated_movie_data %>%
  ggplot(aes(x = Year, y = Total_Film_Count)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Total Number of Films by Year", x = "Year", y = "Total Number")

print(plot_total_film_count_per_year)

# Correlasion Analysis for Question 3d (I got AI help here)
cor_votes_rating <- cor(combined_movie_data$Votes, combined_movie_data$Rating, use = "complete.obs")
print(paste("Votes and Rating Correlation:", cor_votes_rating))

# Scatter plot
plot_votes_rating <- combined_movie_data %>%
  ggplot(aes(x = Votes, y = Rating)) +
  geom_point() +
  theme_minimal() +
  scale_x_log10() +  
  labs(title = "Votes vs Rating", x = "Votes (log scale)", y = "Rating")

print(plot_votes_rating)

# Correlation Analysis for Question 3d(I got AI help here) 
cor_duration_rating <- cor(combined_movie_data$Duration, combined_movie_data$Rating, use = "complete.obs")
print(paste("Duration and Rating Correlation:", cor_duration_rating))

# Scatter plot
plot_duration_rating <- combined_movie_data %>%
  ggplot(aes(x = Duration, y = Rating)) +
  geom_point() +
  theme_minimal() +
  labs(title = "Duration vs Rating", x = "Duration (minutes)", y = "Rating")

print(plot_duration_rating)

```

# The Answers

## Question 3

**3a. Arrange your data frame in descending order by Rating. Present the top 5 and
bottom 5 movies based on user ratings. Have you watched any of these movies? Do
you agree or disagree with their current IMDb Ratings?**

*I watched "Mucize" and I think it deserves the leading place, but I can't say anything about the other top 5 and below5 because I haven't watched them yet.*
**3b. Check the ratings of 2-3 of your favorite movies.**

*The code is above.*
**3c. Considering that audience rating is a crucial indicator of movie quality, what can
you infer about the average ratings of Turkish movies over the years? Calculate yearly
rating averages and plot them as a scatter plot. Hint: Use functions like group_by(),
summarise(), mean(), ggplot(), geom_point(). Similarly, plot the number of
movies over the years. You might observe that using yearly averages could be misleading due to the increasing number of movies each year. As an alternative solution,
plot box plots of ratings over the years (each year having a box plot showing statistics
about the ratings of movies in that year). What insights do you gather from the box
plot?**

*I initially calculated the average ratings of Turkish movies by year and used a scatter plot to visualize the data. However, I realized that this could be misleading due to the increasing number of movies each year.*

*To address this, I switched to using box plots, which better show the spread, median, and outliers for each year. This provided a more nuanced view, revealing how ratings vary and are distributed across different years in Turkish cinema.*
**3d. Do you believe there is a relationship between the number of votes a movie received
and its rating? Investigate the correlation between Votes and Ratings.**

*I calculate the correlation between the number of votes and the rating. A positive correlation indicates that movies with more votes tend to have higher ratings, but this is not always the case, especially with movies that have fewer votes but high ratings.* **3e. Do you believe there is a relationship between a movie’s duration and its rating?
Investigate the correlation between Duration and Ratings.**

*I calculate the correlation between the duration and the rating. If the correlation is low, it suggests that the movie's length does not significantly impact its rating.*

## Question 4

You can see the code for question 4 below. And for the answer of the question: "Are these the same first high-rated 11 movies in your initial data frame?"
*The answer is no they are not the same. I think if the movies do not match because, IMDb does not use ratings alone to determine the rankings of its Top 1000 movie list, and that the ranking is a more complex combination of several factors.*

```{r}

url_top_1000_turkish <- "https://www.imdb.com/search/title/?title_type=feature&groups=top_1000&country_of_origin=TR&sort=num_votes,desc"

scrape_turkish_top_1000_data <- function(url) {
  page <- read_html(url)
  
  titles <- page %>% html_nodes(".ipc-title__text") %>% html_text()
  years <- page %>% html_nodes(".dli-title-metadata-item:nth-child(1)") %>% html_text()
  
  # Clean and match lengths
  max_length <- max(length(titles), length(years))
  titles <- rep(titles, length.out = max_length)
  years <- rep(years, length.out = max_length)
  
  # Create DataFrame with Title and Year
  movie_data <- tibble(
    Title = titles,
    Year = years
  )
  
  return(movie_data)
}

# Fetching the data for Turkish top 1000 movies
turkish_top_1000_data <- scrape_turkish_top_1000_data(url_top_1000_turkish)

# Merge the data to add Duration, Rating, and Votes to the Turkish Top 1000 DataFrame
merged_movie_data <- left_join(turkish_top_1000_data, combined_movie_data, by = c("Title", "Year"))

# Step 1: Sort the 11 Turkish Top 1000 movies by their IMDb Rank (using Rating as a proxy)
sorted_turkish_top_1000_by_rank <- merged_movie_data %>%
  arrange(desc(Rating)) %>%
  head(11)

# Step 2: Get the top 11 highest-rated movies from the initial data frame
top_rated_movies_from_initial <- combined_movie_data %>%
  arrange(desc(Rating)) %>%
  head(11)

# Step 3: Print and compare both lists
print("Top 11 Ranked Turkish Movies by IMDb Rank:")
print(sorted_turkish_top_1000_by_rank)

print("Top 11 Highest-Rated Movies from the Initial Data Frame:")
print(top_rated_movies_from_initial)

# Analysis: Check if the lists match(I got AI help to make this part better:)
if(identical(sorted_turkish_top_1000_by_rank$Title, top_rated_movies_from_initial$Title)) {
  print("The top 11 ranked movies are the same as the highest-rated 11 movies.")
} else {
  print("The top 11 ranked movies are not the same as the highest-rated 11 movies.")
}
```
